Certified Symbolic Finite Transducers: Formalization and Applications to String Analysis

### 2025-12-03 Paper/formalization.tex
fix errors

Figure \ref{fig-compute-nft-product} illustrates the algorithm \texttt{productT\_impl}, which is implemented using the \emph{Refine\_Monadic} framework. Note that in the implementation, there are some refined operations:  \texttt{nfa\_states}, \texttt{nfa\_trans}, \texttt{nfa\_initial}, \texttt{nfa\_accepting},
and \texttt{nft\_tranfun}. These are corresponding to the states, transitions, initial states, accepting states, and output function mapping of the SFT.

@@

    We now present the implementation of \texttt{subtrans\_comp} in detail, as shown in Figure \ref{fig-def-subtrans_comp} (the implementation of \texttt{subtrans\_comp\_$\varepsilon$} follows analogous principles). For a transtion $(q, (\text{Some}~\alpha, f), q')$ in the SFT, this function traverses all transitions in the SFA, represented by the set \texttt{T}. For each transition $(q_1, \alpha', q_1')\in \texttt{T}$, the function performs two key operations when the intersection of input labels is non-empty ($\alpha \cap \alpha' \neq \emptyset$, verified using \texttt{nemptyIs}):

>>>>

Figure \ref{fig-compute-nft-product} illustrates the algorithm \texttt{productT\_impl}, which is implemented using the \emph{Refine\_Monadic} framework. Note that in the implementation, there are some refined operations:  \texttt{nfa\_states}, \texttt{nfa\_trans}, \texttt{nfa\_initial}, \texttt{nft\_tranfun},
and \texttt{nfa\_accepting}. These are corresponding to the states, transitions, initial states, accepting states, and output function mapping of the SFT.

@@

    We now present the implementation of \texttt{subtrans\_comp} in detail shown in Figure \ref{fig-def-subtrans_comp} (\texttt{subtrans\_comp\_$\varepsilon$} follows analogous principles). For a transtion $(q, (\text{Some}~\alpha, f), q')$ in the SFT, this function traverses all transitions in the SFA, represented by the set \texttt{T}. For each transition $(q_1, \alpha', q_1')\in \texttt{T}$, the function performs two key operations when the intersection of input labels is non-empty ($\alpha \cap \alpha' \neq \emptyset$, verified using \texttt{nemptyIs}):

### 2025-12-03 Paper/main.tex
Changed institutes
Removed dept
Added ack
minor update
fix errors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{Shuanglong Kan}
\orcid{0000-0002-4132-2626}
\affiliation{%
  \department{ Verified System Design Automation Group}
  \institution{Barkhausen Institut}
  \city{Dresden}
  \country{Germany}
}
\email{shuanglong.kan@barkhauseninstitut.org}

\author{Anthony W. Lin}
\orcid{0000-0003-4715-5096}
\affiliation{
  \department{Department of Computer Science}
  \institution{University of Kaiserslautern-Landau \& MPI-SWS}
  \city{Kaiserslautern}
  \country{Germany}
}
\email{awlin@mpi-sws.org}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The following is specific to CPP '26 and the paper
%%% 'Certified Symbolic Finite Transducers: Formalization and Applications to String Analysis'
%%% by Shuanglong Kan and Anthony W. Lin.
%%%
\acmDOI{10.1145/3779031.3779094}
\acmYear{2026}
\copyrightyear{2026}
\acmISBN{979-8-4007-2341-4/2026/01}
\acmConference[CPP '26]{Proceedings of the 15th ACM SIGPLAN International Conference on Certified Programs and Proofs}{January 12--13, 2026}{Rennes, France}
\acmBooktitle{Proceedings of the 15th ACM SIGPLAN International Conference on Certified Programs and Proofs (CPP '26), January 12--13, 2026, Rennes, France}
\received{2025-09-12}
\received[accepted]{2025-11-13}

@@

\author{Shuanglong Kan}
\orcid{0000-0002-4132-2626}
\affiliation{%
  \institution{Barkhausen Institute}
  \city{Dresden}
  \country{Germany}
}
\email{shuanglong.kan@barkhauseninstitut.org}

\author{Anthony W. Lin}
\orcid{0000-0003-4715-5096}
\affiliation{
  \institution{Max-Planck Institute for Software Systems}
  \institution{TU Kaiserslautern}
  \city{Kaiserslautern}
  \country{Germany}
}
\email{awlin@mpi-sws.org}

@@

\paragraph{Acknowledgment.} We thank Hongjian Jiang and Philipp Rümmer for the
discussion. The authors are supported by European Research Council (LASD, 
grant number 101089343).
